Variational Monte Carlo on bosonic systems

### 2018-02-07 project_1/article/article.tex
Add proper substitution for the nabla operator
Add explicit expression for the Laplacian

            We now find the Laplacian of the trial wavefunction by taking the
            gradient of \autoref{eq:gradient_full_wavefunction}.

@@

            variable substitution. We replace the derivative of the radial

>>>>

            We now find the Laplacian of the trial wavefunction by finding the
            divergence of \autoref{eq:gradient_full_wavefunction}.

@@

            variable substitution using $r_{km} = |\vf{r}_k - \vf{r}_m|$. We can
            then rewrite the $\nabla_k$-operator as
                \dpd[]{r_{km}}{r_{km}}
                \nabla_k r_{km} \dpd[]{}{r_{km}}
                \frac{\vf{r}_k - \vf{r}_m}{r_{km}}\dpd[]{}{r_{km}}.
            Applying this version of the $\nabla_k$-operator to $u_{km}$ yields
                \frac{\vf{r}_k - \vf{r}_m}{r_{km}}
                \dpd[]{u_{km}}{r_{km}}.
            For the Laplacian we switch a little back and forth between the two
            ways of representing the $\nabla_k$-operator. We thus get
                    \nabla_k^2 u_{km}
                    \frac{\nabla_k \vf{r}_k}{r_{km}}\dpd[]{u_{km}}{r_{km}}
                        \nabla_k \frac{1}{r_{km}}
                    (\vf{r}_k - \vf{r}_m)\dpd[]{u_{km}}{r_{km}}
                    + \frac{\vf{r}_k - \vf{r}_m}{r_{km}}
                    \nabla_k \dpd[]{u_{km}}{r_{km}} \\
                    &= \frac{d}{r_{km}}\dpd[]{u_{km}}{r_{km}}
                    - \frac{(\vf{r}_k - \vf{r}_m)^2}{r_{km}^3}
                    \dpd[]{u_{km}}{r_{km}}
                    + \frac{(\vf{r}_k - \vf{r}_m)^2}{r_{km}^2}
                    \dpd[2]{u_{km}}{r_{km}} \\
                    \frac{d - 1}{r_{km}}\dpd[]{u_{km}}{r_{km}}
                    + \dpd[2]{u_{km}}{r_{km}},
                where $d$ is again the dimensionality of the problem. In total
                we can state an intermediate version of the local energy as
                    \frac{\vf{r}_k - \vf{r}_m}{r_{km}}
                    \dpd[]{u_{km}}{r_{km}}
                    + \sum_{m\neq k}^N
                        \frac{d - 1}{r_{km}}\dpd[]{u_{km}}{r_{km}}
                        + \dpd[2]{u_{km}}{r_{km}}
                    \sum_{m, n \neq k}^N
                    \frac{\vf{r}_k - \vf{r}_m}{r_{km}}
                    \frac{\vf{r}_k - \vf{r}_n}{r_{kn}}
                    \dpd[]{u_{km}}{r_{km}}
                    \dpd[]{u_{kn}}{r_{kn}}.
